\documentclass[conference]{IEEEtran}
\IEEEoverridecommandlockouts
% The preceding line is only needed to identify funding in the first footnote. If that is unneeded, please comment it out.
\usepackage{cite}
\usepackage{hyperref}
\usepackage{amsmath,amssymb,amsfonts}
\usepackage{algorithmic}
\usepackage{graphicx}
\usepackage{textcomp}

\usepackage[table]{xcolor}
\usepackage{tikz}
\usetikzlibrary{positioning, shapes.geometric, fit}
\usepackage{siunitx}
\usepackage{soul}
\usepackage{listings}
\def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
    T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}

\input{preamble}
\begin{document}
\include{commands}

\title{Runtime Verification of Autonomous Systems utilizing Digital Twins as a Service
    \thanks{%
        The work presented here is partially supported by the RoboSAPIENS project funded by the European Commission's Horizon Europe programme under grant agreement number 101133807, the O5G-N-IoT project, funded by the German Federal Ministry for Economic Affairs and Climate Action, due to a resolution of the German Bundestag,  % O5G-N-IoT corresponds to Iven, Leucker and Vosteen from Lübeck 
        and the SM4RTENANCE project under grant no. 101123423. % Eduard
    }
}

\author{
\IEEEauthorblockN{Morten~Haahr~Kristensen\IEEEauthorrefmark{1},
Alberto~Bonizzi\IEEEauthorrefmark{2},
Cl\'{a}udio~Gomes\IEEEauthorrefmark{1},
Simon~Thrane~Hansen\IEEEauthorrefmark{3},
Carlos~Isasa\IEEEauthorrefmark{1},\\
Hannes~Iven\IEEEauthorrefmark{4},
Eduard~Kamburjan\IEEEauthorrefmark{5},
Peter~Gorm~Larsen\IEEEauthorrefmark{1},
Martin~Leucker\IEEEauthorrefmark{4},
Prasad~Talasila\IEEEauthorrefmark{1},\\
Valdemar~Trøjgård~Tang\IEEEauthorrefmark{1},
Stefano~Tonetta\IEEEauthorrefmark{2},
Lars~B.~Vosteen\IEEEauthorrefmark{4},
Thomas~Wright\IEEEauthorrefmark{1}}
\IEEEauthorblockA{\IEEEauthorrefmark{1}\textit{Department of Electrical and Computer Engineering} \\
    \textit{Aarhus University, Denmark}\\
    \{mhk, claudio.gomes, cisasa, pgl, prasad.talasila, valdemar.tang, thomas.wright\}@ece.au.dk}
\IEEEauthorblockA{\IEEEauthorrefmark{2}\textit{Fondazione Bruno Kessler, Italy} \\
    \{bonizzi,tonettas\}@fbk.eu}
\IEEEauthorblockA{\IEEEauthorrefmark{3}\textit{Interdisciplinary Centre for Security, Reliability and Trust} \\
    \textit{University of Luxembourg}\\
    simon.hansen@uni.lu}
\IEEEauthorblockA{\IEEEauthorrefmark{4}\textit{Institute for Software Engineering and Programming Languages} \\
    \textit{Universität zu Lübeck, Germany}\\
    hannes.iven@student.uni-luebeck.de, \{leucker,vosteen\}@isp.uni-luebeck.de}
\IEEEauthorblockA{\IEEEauthorrefmark{5}\textit{Department of Informatics,  Norway,} \\
    \textit{University of Oslo, Norway}\\
    eduard@ifi.uio.no}
}

\maketitle

\begin{abstract}
    Autonomous systems (AS) enable systems to adapt to drastic and unprecedented environmental changes, a capability that can be complimented through the utilization of Digital Twins (DTs).
    However, the additional capabilities of AS come at the cost of explainability, as the expanding adaptation space complicates reasoning about the system's behavior.
    For certain types of systems, it is crucial to ensure that specific properties are upheld despite the system's autonomous behavior.
    To facilitate the monitoring of these properties, we propose the use of Runtime Verification (RV).
    This tutorial demonstrates the integration of RV tools into a Digital Twins as a Service (DTaaS) platform to monitor and verify the behavior of AS in real-time.
    By exploring various methods to incorporate RV tools within a DT context, the tutorial aims to advance the application of RV technologies in autonomic computing and self-adaptive system design.
    Specifically, we demonstrate how the behavior of a self-configuring DT is verified utilizing RV.
    This is accomplished through the DTaaS platform, which supports seemless deployment of DT-based AS.
\end{abstract}

\begin{IEEEkeywords}
    Self-adaptivity, runtime verification, digital twins, monitor, TeSSLa, NuRV
\end{IEEEkeywords}

\input{sections/introduction}%
\input{sections/background.tex}%
% \input{sections/methodology.tex}%
\input{sections/examples/introduction.tex}
\input{sections/examples/incubator.tex}
\input{sections/examples/nurv.tex}
\input{sections/examples/tessla.tex}
\input{sections/conclusion}%

\bibliographystyle{splncs04}
\bibliography{bibliographies/common.bib}

\end{document}
